\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 prelims.tex
.

@@

We define the PWA transition system as a transition system
$\rho:\tupleof{\pLocs,\pVars,\scrT, \pLocI,\Theta}$, where $\pLocs$ is
a nonempty set of locations, $\pVars$ is a set of variables, $\scrT$
is a finite subset of $\pLocs \times \pLocs$, and each transition
$\tau \in \scrT$ is associated with a transition relation of the form
\[
    \rho_{\tau}(\pVar,\pVar') \subseteq \setof{(\pVar,\pVar')) \;|\;
    g_\tau(\pVar) \land g'_\tau(\pVar') \land f_{\tau}(\pVar, \pVar')}
\]
where $f_{\tau}$ is an affine relation on the pre and post states
$\pVar,\pVar'$, $g_{\tau}$ and $g'_{\tau}$ are affine guards (pre and
post conditions) on the states. Finally, $\pLocI$ is an initial
location $\Theta$ is an affine assertion characterizing the initial
states included in $\pLocI$.

>>>>

% A configuration of the PWATS is
% a pair (l,\nu(v)), where \nu is a valuation function assigning values to
% variables.

% A run of the PWA TS is as follows: the PWA TS starts in the initial
% location from a valuation \nu(v) \in theta.

% A move of the PWA TS is described by the function mu: from (L,R^n) to
% (L,R^n), and mu follows the rules that
% mu(l,\nu(v)) = (l',\nu'(v)), iff (l,g,g',f,l') in T, and
% \nu(v) satisfies g, \nu(v') satisfies g', and \nu(v') = f(\nu(v)).

@@

We define the PWA transition system as a discrete transition system
$\rho:\tupleof{\pLocs,\vx,\scrT, \pLocI,\Theta}$, where $\pLocs$ is
a nonempty set of locations, $\vx$ is a set of variables, $\scrT$
is a finite set of transitions of the form $\tupleof{l, \tau,
l'}$, where $l\in\pLocs$ is the pre-location, $l'\in\pLocs$ the
post-location and $\tau(\vx,\vx') \in \scrT$ is the transition. $\tau$
is labled by the transition relation $\rho_{\tau}$
over the current states and the next states. The transition relation
is defined in terms of affine predicates on the current and next
states and an affine update between them.
\[
    \rho_{\tau}(\vx,\vx') \subseteq \setof{(\vx,\vx')) \;|\;
    g_\tau(\vx) \land g'_\tau(\vx') \land f_{\tau}(\vx, \vx')}
\]
where $f_{\tau}$ is an affine relation on the pre and post states
$\vx,\vx'$, $g_{\tau}$ and $g'_{\tau}$ are affine guards (pre and
post conditions) on the states. Finally, $\pLocI$ is an initial
location $\Theta$ is an affine assertion characterizing the initial
states included in $\pLocI$.
